
Chapter 3 - Pendency AND Disposal

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	eval=FALSE,
	message = FALSE,
	warning = FALSE
)
source(here::here("scripts","source_files.R"))
```

Chart 3.1 and 3.2 - State-wise Pendency and Disposal
```{sql connection=con}

select state_name, pending_cases, disposed_cases, (pending_cases::decimal/(pending_cases+disposed_cases)) * 100 as pending_percent, 
(disposed_cases::decimal/(pending_cases+disposed_cases)) * 100 as pending_percent from (
select state_name, count(case when disp_nature = '0' then 1 end) as pending_cases, 
count(case when disp_nature != '0' then 1 end) as disposed_cases from case_details
where case_flag='1' group by state_name) as a
```
Table 3.1 - Court Caseload per year
(New cases registered in a year + Pending cases from previous year)

```{sql connection=con, output.var=reg_by_year}
select state_name, reg_year_date as year, count(*) as registered_cases from case_details
where case_flag='1' and state_name='Assam' group by state_name, reg_year_date order by reg_year_date
```

```{sql connection=con, output.var=disposal_by_year}
select a.state_name, a.year_disposal::varchar as year, count(*) as disposed_cases from (select state_name, DATE_PART('year', date_of_decision::date) as year_disposal from case_details where case_flag='1' and state_name='Assam' and disp_nature!='0') as a group by state_name, year_disposal order by year_disposal
```

```{r case_load_dataset}
court_case_load <- left_join(reg_by_year, disposal_by_year, by=NULL) 
court_case_load[is.na(court_case_load)] <- 0
court_case_load$state_name <- NULL

if(!2012 %in% court_case_load$year){
  court_case_load <- bind_rows(court_case_load, data.frame('year'='2012', 'registered_cases'=0, disposed_cases=0))
}

court_case_load <- court_case_load %>% arrange(year)
court_case_load <- court_case_load[court_case_load$year>=2012,]
year_seq <- seq(2012, 2020)
court_load <- c()
court_case_load$registered_cases_new <- court_case_load$registered_cases 
for(i in 1:length(year_seq)){
 rc <- court_case_load$registered_cases_new[court_case_load$year == year_seq[i]]
 dc <- court_case_load$disposed_cases[court_case_load$year == year_seq[i]]
  
 if(year_seq[i]=='2012'){
   pca <- 0
 } else {
    rcp <- court_case_load$registered_cases_new[court_case_load$year == year_seq[i-1]]
    dcp <- court_case_load$disposed_cases[court_case_load$year == year_seq[i-1]]
    pca <- rcp-dcp
 }
  
 court_load[[i]] <- rc+pca
 court_case_load$registered_cases_new[i] <- court_load[[i]]
}

court_case_load
```

Check for an Assam case that where the date of registration is from 2010 and the reg_year is 2016
```{sql connection=con}
select * from case_details where case_flag='1' and state_name='Assam' and reg_year_date <= '2012'
```
Chart 3.3 - Trend for Fresh Cases and Cases Carried Forward from Previous Year - 2012 to 31 March 2020

```{sql connection=con, output.var=reg_by_year}
select reg_year_date as year, count(*) as registered_cases from case_details
where case_flag='1' group by reg_year_date order by reg_year_date
```

```{sql connection=con, output.var=disposal_by_year}
select a.year_disposal::varchar as year, count(*) as disposed_cases from (select state_name, DATE_PART('year', date_of_decision::date) as year_disposal from case_details where case_flag='1' and disp_nature!='0') as a group by year_disposal order by year_disposal
```

```{r case_load_dataset}
court_case_load <- left_join(reg_by_year, disposal_by_year, by=NULL) 
court_case_load[is.na(court_case_load)] <- 0
court_case_load$state_name <- NULL

if(!2012 %in% court_case_load$year){
  court_case_load <- bind_rows(court_case_load, data.frame('year'='2012', 'registered_cases'=0, disposed_cases=0))
}

court_case_load <- court_case_load %>% arrange(year)
court_case_load <- court_case_load[court_case_load$year>=2012,]
year_seq <- seq(2012, 2020)
court_load <- c()
court_case_load$registered_cases_new <- court_case_load$registered_cases 
for(i in 1:length(year_seq)){
 rc <- court_case_load$registered_cases_new[court_case_load$year == year_seq[i]]
 dc <- court_case_load$disposed_cases[court_case_load$year == year_seq[i]]
  
 if(year_seq[i]=='2012'){
   pca <- 0
 } else {
    rcp <- court_case_load$registered_cases_new[court_case_load$year == year_seq[i-1]]
    dcp <- court_case_load$disposed_cases[court_case_load$year == year_seq[i-1]]
    pca <- rcp-dcp
 }
  
 court_load[[i]] <- rc+pca
 court_case_load$registered_cases_new[i] <- court_load[[i]]
}

court_case_load
```

```{r}

court_case_load$cases_fwd <- court_case_load$registered_cases_new - court_case_load$registered_cases
court_case_load$case_fwd_percent <- round(court_case_load$cases_fwd/court_case_load$registered_cases_new * 100,2)
court_case_load

```

Table 3.3 - Court Caseload - Top 20 per cent Districts

```{sql connection=con}
select district_name, (cases_registered_2020+cases_before_2020) as case_load_2020 from (select district_name, count(case when reg_year_date='2020' then 1 end) as cases_registered_2020, count(case when reg_year_date<'2020' and (DATE_PART('year', date_of_decision::date)>='2020' OR disp_nature='0') then 1 end)  as cases_before_2020  from case_details where case_flag='1' and state_name='Haryana' group by district_name) as a order by case_load_2020 desc
```

Offence wise analysis

```{r}
offence_data <- read_csv(here("research","datasets","case_wise_offence.csv"))
offence_data$state <- stringr::str_sub(offence_data$cino,start = 1,end = 2)
```

```{sql connection=con, output.var='case_status'}
select cino, disp_nature from case_details where case_flag='1'
```

```{r}
offence_data <- left_join(offence_data, case_status, by='cino')
offence_data$case_status <- ifelse(offence_data$disp_nature!=0,'disposed','pending')
```


```{sql connection=con}
select * from case_details where cino='DLWT010016612014'
```



