
[Queries and Challenges document](https://docs.google.com/document/d/1lF_5ieLHunm-IRQDA1tDk_QkSJUbWYENTRU13WjyepY/edit)

```{r setup, include=FALSE}
# knitr::opts_chunk$set(
# 	echo = FALSE,
# 	eval=FALSE,
# 	message = FALSE,
# 	warning = FALSE
# )
source(here::here("scripts","source_files.R"))
```

The E-Courts portal shows that there are 21 District Courts as against 18 this report looks at. See https://districts.ecourts.gov.in/haryana and https://highcourtchd.gov.in/sub_pages/top_menu/dist_jud/pdf/Haryana_Gradation1.pdf

How do we explain this?

Missing districts:

- Karnal
- Mahendragarh
- Mewat

[Data Mining statistics from Haryana](https://docs.google.com/spreadsheets/d/1CXfaxY5v4FJB0chdo--fW_EsX353Bi6mZzzEScguCkI/edit#gid=689112034)

On e-Courts website:
- Narnaul district is displayed as Mahendragarh
- Nuh district is displayed as Mewat

We have data from both these districts. Checking the number of flagged cases from these districts. 

```{sql connection=con, output.var='haryana_district_wise_cases'}
select state_name, district_name, case_flag, count(cino) from case_details where state_name='Haryana' group by state_name, district_name, case_flag
```


```{r}
haryana_case_details <- haryana_district_wise_cases %>% pivot_wider(names_from = 'case_flag', values_from='count', names_prefix='case_flag_')
haryana_case_details$total_cases <- haryana_case_details$case_flag_1 + haryana_case_details$case_flag_0
```

Insights:

- All 36 cases from Karnal were not considered in the master list of cases because of invalid case types
- All 55 cases from Narnaul (Mahendragarh) were not considered in the master list of cases because of invalid case types
- We did not find any case on the e-Courts portal at the time of mining from Nuh (Mewat)


```{sql echo=FALSE, connection=con}
select type_name, count(cino), state_name from case_details where district_name IN ('Narnaul','Karnal') group by type_name, state_name
```

```{sql connection=con}
select * from case_details where district_name IN ('Narnaul','Karnal') AND type_name='POCSO ACT'
```


